---
title: "Homework 1"
author: "Ayberk AKIN 19080575"
output:
  html_document:
    df_print: paged
---

```{r global_options, include=FALSE}
# Do not delete or modify this chunk.
# We will cover chunk options later.
# This is required for Question 7
library(knitr)
opts_chunk$set(fig.align="center", fig.height=4, fig.width=5.5)
```

**Question 1** With Markdown write a sentence that has one word in bold.

Turkey have a  __high inflation__ 

**Question 2** With Markdown write a sentence that has one word in italic.

Turkey have a  _high inflation_

**Question 3** With Markdown write a sentence that has one word in italic bold.

Turkey have a  **_high inflation_**

**Question 4** With Markdown write an unordered list with three items.

*credit card
*deposity
*loans

**Question 5** With Markdown write an ordered list with three items.
1.credit card
2.deposity
3.loans

**Question 6** With Markdown give a link to your favorite webpage.

[treadingview!](https://tr.tradingview.com/)

**Question 7** With Markdown add a cat picture.

[Cat!](https://cdn.pixabay.com/photo/2020/11/15/18/31/cat-5746771_960_720.png)

**Question 8** With Rmarkdown insert a code chunk and give an example of a simple mathematical calculation in it.

Here is some text in your Rmarkdown document.

```{r}
# Inserting a code chunk
x <- 5
y <- 7
z <- x + y
z
```

**Question 9** With $LaTeX$ write your favorite equation in block form.

Here is some text in your R Markdown document.

$$
e^{i\pi} + 1 = 0
$$


**Question 10** In a code chunk calculate 3 + 4.

```{r}
# Calculating 3 + 4
3 + 4
```
